---
title: "FR+A Report Generator"
output: 
  word_document:
    reference_docx: data/fra-template.docx
date: "2023-12-30"
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
datapath <- "data/"
imgpath <- "images/"
knitr::opts_chunk$set(echo = FALSE)
library(magrittr)
library(officer)
library(officedown)
library(dplyr)
library(toOrdinal)
source("r_docs/R/styles_variables_functions.R")
source("r_docs/R/footnotes.R")
source("r_docs/R/intro_parts.R")
source("r_docs/R/background_facts_med_hx.R")
source("r_docs/R/general_comments.R")
source("r_docs/R/inj_biomech.R")
source("r_docs/R/signature_block_appendix.R")
# table for reading styles
styles_tab <- styles_info(doc)
```

```{r loop fpar add function}
block_add_fun <- function(x, blocklist, style = "Normal") {
  for (i in length(blocklist):1) {
    body_add(x, blocklist[[i]], style = style)
  }
  return(x)
}

block_add_style_fun <- function(x, list) {
  for (i in length(list$content):1) {
    block_add_fun(x, blocklist = list$content[[i]], style = list$style[[i]])
  }
  return(x)
}

block_add_fps_fun <- function(x, list) {
  for (i in length(list):1) {
    for (j in length(list[[i]]):1) {
      body_add(x, list[[i]][[j]], style = list[[i]][[j]]$style)
    }
  }
  return(x)
}
```

## reference for replacing grammar in report language:

Mr_Ms_Lastname()/Firstname_Lastname() - defaults to plaintiff; otherwise argument will be "defendant" or "lawyer" - includes all plaintiffs,
genders for single and naturalizes language for multiple

he_she()/He_She() him_her()/Him_Her() his_her()/His_Her() - defaults to
plaintiff; otherwise argument will be "defendant" or "lawyer"

single_plural() - argument ("in quotes") will be single if
length(plaintiff\$first_name) == 1, otherwise pluralize - pluralizes
verbs too (is, isn't, was, wasn't, has, hasn't)
added "it" -> "they" which is not ideal because could be they or them

```{r separate and alter external docx documents}
# # Load the existing Word document
# doc_split <- read_docx(background_facts_recon_file_name)
# 
# # Get the document's blocks
# content <- docx_summary(doc_split)
# 
# # Find the position where the document says "Reconstruction"
# split_position <- NULL
# for (i in seq_len(nrow(content))) {
#   if (grepl("Reconstruction", content$text[i])) {
#     split_position <- i
#     break
#   }
# }
# 
# if (is.null(split_position)) {
#   stop("Text 'Reconstruction' not found in the background facts/reconstruction document.")
# }
# 
# # Split the document into two parts
# part1 <- block_list(doc_split)[1:(split_position - 1)]
# part2 <- block_list(doc_split)[split_position:nrow(content)]
# 
# # Create new documents for each part
# doc1 <- read_docx()
# doc2 <- read_docx()
# 
# # Add blocks to each document
# for (block in part1) {
#   doc1 <- body_add(doc1, block)
# }
# for (block in part2) {
#   doc2 <- body_add(doc2, block)
# }
# 
# # Write each part into separate Word documents
# print(doc1, target = "background_facts.docx")
# print(doc2, target = "reconstruction.docx")

```


```{r test full doc build code}
# the idea here is to have an entry after each report element that appends to a list that updates and doesn't duplicate. then the block_add_style_fun() function will take each element, apply the associated $style value, and put it through the block_add_fun() function.

# Style guide for block_add_style_fun() function
# "Normal": at least 16 pt line spacing; majority doc style
# "Body Text 2": Single line spacing and 3.75 tab distance
# "Author": block quote style indentation on both sides
# "Definition": bullet point in summary
# "Body Text 3": inverted indent in injury biomech section
# "caption": size 9, bold, justified, margins 2.25 in from both sides, for biomech image description subtitles
# "Subtitle": (for images and crash summary image descriptions) size 10, bold, centered, margins 2.25 in from both sides
# "footnote text": invisible for footnotes (when more than 2 in one text)
# "Author": size 10, everything else Normal (for signature block)


caus_doc_rear_disk_build <- list(
  heading,
  qualifications$causation,
  background_facts$causation,
  inj_biomech$meat$caus$rear$disk
)

# current job: make new entries for invisible footnote text and make invisible style in word template
caus_doc_rear_shoulder_build <- list(
  heading, 
  background_facts$causation,
  inj_biomech$meat$caus$rear$shoulder
)

caus_doc_near_side_disk_build <- list(
  heading, 
  background_facts$causation,
  inj_biomech$meat$caus$near_side$disk,
  three_steps$causation$disk,
  signature_block
)

caus_doc_near_side_shoulder_build <- list(
  heading, 
  background_facts$causation,
  inj_biomech$meat$caus$near_side$shoulder
)

rebut_doc_build <- list(
  heading, 
  background_facts$rebuttal,
  inj_biomech$meat$rebuttal,
  three_steps$rebuttal$all_experts,
  signature_block
)


notes_doc_build <- list(
  heading, 
  background_facts$notes)

caus_doc_build <- list(
  heading,
  receipt,
  purpose$causation$general,
  qualifications$causation,
  background_facts$causation,
  signature_block,
  appendix$causation$general
)
```

```{r final doc build function call}
# define doc-build list that will be run
doc_build_final <-
  if (
    doc_type == "notes") notes_doc_build else if (
      doc_type == "causation") caus_doc_build


#fps function call
doc %>%
  cursor_begin() %>%
  body_remove() %>%
  #block_pour_docx("sample_med_hx.docx") %>%
  block_add_fps_fun(caus_doc_build) %>%
  print(target = "FRA-report-output.docx")

```

```{r final build}
# Heading

# Lawyer address

# Intro paragraph

# The Purpose of this Report

# Summary Opinions (rebuttal)

# Qualifications

# Background Facts

# Medical History

# General Comments on Expert (rebuttal)

# Injury Biomechanics intro

# Injury Biomechanics body

# 3 steps alternative explanations (Causation)

# Rebuttal points

# Conclusions

# Signature Block

# Appendix

```
